Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-07-08 paper/main.tex
how to write result & discussion as comments

% Titel-Vorgabe < 110 chars incl. spaces
%  jetzt 109 Chars
\title{Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description}

@@

\todo[inline]{I consider tables of significant clusters for every contrast as
overkill. One contrast, the ``primary contrast'', appropriate.}

\subsection{stability contrasts}
The overlap of significant clusters of the 7 (well actually 8) contrast for the
audio-description, and 5 contrasts computed for the movie can be found in Figure
\ref{fig:stability-slices}.

% AO
\todo{alle noch einmal im einzelnen angucken; was ist mit COPE 8, der ist in der
Abb. nicht drin; zeigt (noch) einer keine sign. cluster?}
% PPA
Six of seven AO contrasts show significant bilateral clusters in anterior
regions of the group PPA overlap (which is temporal occipital fusiforim gyrus
regarding to co-registered Harvard-Oxford Cortical Structural Atlas).
% Precuneus = Retro Spenial Cortex ?
Six of seven contrasts show significant clusters in the ventral precuneus /
retrospenial cortex (RSC)

% AV
% PPA
All five AV contrasts yielded significant bilateral clusters in (temporal)
occipital, fusiform cortex showing congruency with the group overlap of
individual PPA ROIs.
% Lingual Gyrus
Homologous clusters of three contrasts extend further into lingual gyrus.
% RSC
Three contrasts show significant bilateral clusters in RSC.
% LOC
Four contrasts show signficant bilateral clusters in laterial occipital cortex

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/stability-slices}
    \caption{Stability of contrasts. Overlap of significant clusters (Z>3.4;
        p<.05, cluster corrected) of contrasts created to isolate the PPA. Blue:
        contrasts 1-7 (see Table \ref{tab:ao-contrasts} for the
    audio-description.}. Red: contrasts 1-5 (see Table \ref{tab:av-contrasts}
    for the audio-visual movie. Black: outline of overlapping individual PPA
    ROIs \citep{sengupta2016extension}.  \label{fig:stability-slices}
\end{figure*}

\subsection{primary contrasts}
See Figure \ref{fig:group-slices}.

AO stimulus; See Table \ref{tab:res-ao-group1}

AV stimulus; See Table \ref{tab:res-av-group1}

\begin{table*}[t]
    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast \texttt{geo, groom > all non-geo} (audio-only stimulus).
Clusters sorted by voxel size.
The first brain structure given contains the voxel with the maximum Z-Value, followed by brain structures from posterior to anterior, and partially covered areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
\label{tab:res-ao-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
188 & 5.96E-08 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l. precuneus \\
164 & 2.38E-07 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r. precuneus; \\
83 & 0.000128 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & r. temporal (occipital) fusiform c.; posterior parahippocampal g. \\
73 & 0.000318 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & l. lingual g.; temporal (occipital) fusiform g., posterior parahippocampal c. \\
63 & 0.000824 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & r. superior lateral occipital c. \\
37 & 0.0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & l. superior lateral occipital c. \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast \texttt{vse\_new > vpe\_old} (audio-visual stimulus).
Clusters sorted by voxel size.
The first brain structure given contains the voxel with the maximum Z-Value,
followed by brain structures from posterior to anterior, and partially covered
areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
\label{tab:res-av-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r
cuneal c., intracalcarine c., bilaterally occipital fusiform g., temporal fusiform c., posterior parahippocampal c.  \\
154 & 6.56E-07 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
121 & 7.69E-06 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
\bottomrule
\end{tabular}
\end{table*}

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/group-slices}
    \caption{Mixed-effects group-level (N=14) GLM results.  Significant clusters
        (Z>3.4, p<0.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
        head template (grey).
        Light grey: The audio-description's field-of-view
        (cf. \citep{hanke2014audiomovie}).
        Blue: the $t$-contrast comparing
        geometry-related nouns to non geometry-related nouns spoken by the
        audio-description's narrator (geo, groom > all non-geo).
        Red: audio-visual movie (red).}
    \label{fig:group-slices}
\end{figure*}

@@

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
    \caption{individual PPAs}
    \label{fig:subs-thresh-ppa}
\end{figure*}

@@

@@

>>>>

% Titel-Vorgabe < 110 chars incl. spaces
%  jetzt 109 Chars
\title{Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description}

@@

% HOW TO WRITE METHODS SEXTION
% first paragraph (cause most readers don't read methods beforehand
% summarizes the overall approach to the problem outlined in the intro
% key innovative methods that were developed
% -> gist of the methods that were used

% subsequent paragraphs start with a sentence or two
% that set up the question that the paragraph answers
% e.g. ``To verify that there are no artifacts..''
% What is the test-retest reliability of our measure?''
% “We next tested whether Ca2+ flux through Ca2+ channels was involved.''
% Middle of the paragraph presents data and logic that pertain to the question,
% paragraph ends with a sentence that answers the question
% For example, it may conclude that none of potential artifacts were detected.
% Each paragraph convinces the reader of answer given in its last sentence.
% The result of each paragraph is a logical statement

\subsection{primary contrasts}
% AO
The primary $t$-contrast for the audio-description comparing geometry-related
nouns to non geometry-related nouns spoken by the audio-description's narrator
(\texttt{geo, groom > all non-geo} yielded six significant clusters (see Table
\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% precuneus
Two homologous clusters in the ventral precuneus extending into the
retrosplenial cortex.
% PPA
Two homologous clusters in the lingual gyrus, occipital and temporal fusiform
gyrus, and posterior parahippocampal cortex \todo{the clusters are small but
that's what the Harvard-Oxford Atlas suggests, probably because at borders of
the areas}.
% LOC
And finally, two homologous clusters in the superior lateral occipital cortex.

% AV
The primary $t$-contrast for the movie comparing cuts to a new setting with cuts
to a familiar perspective (\texttt{vse\_new > vpe\_old}) yielded three
significant clusters (see Table \ref{tab:res-av-group1}, Figure
\ref{fig:group-slices}).
% LOC
Two clusters in the superior lateral occipital cortex (left bigger than right).
% PPA + others.
And one one cluster spanning across the midline and comprising intracalcarine
and cuneal cortex, lingual gyrus and restrosplenial cortex,  occipital fusiform
gyrus and temporal fusiform gyrus, and parahippocampal cortex bilaterally.

\begin{table*}[t]
    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected)
        of the primary $t$-contrast for the audio-description comparing
        geometry-related nouns to non geometry-related nouns spoken by the
        audio-description's narrator (\texttt{geo, groom > all non-geo}).
        Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
followed by brain structures from posterior to anterior, and partially covered
areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
    \label{tab:res-ao-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
188 & 5.96E-08 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l. precuneus \\
164 & 2.38E-07 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r. precuneus; \\
83 & 0.000128 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & r. temporal (occipital) fusiform c.; posterior parahippocampal g. \\
73 & 0.000318 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & l. lingual g.; temporal (occipital) fusiform g., posterior parahippocampal c. \\
63 & 0.000824 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & r. superior lateral occipital c. \\
37 & 0.0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & l. superior lateral occipital c. \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected)
        of the primary $t$-contrast for the movie comparing cuts to a new
        setting with cuts to a familiar perspective (\texttt{vse\_new >
        vpe\_old}).
Clusters sorted by voxel size.
The first brain structure given contains the voxel with the maximum Z-Value,
followed by brain structures from posterior to anterior, and partially covered
areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
\label{tab:res-av-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r
cuneal c., intracalcarine c., bilaterally occipital fusiform g., temporal fusiform c., posterior parahippocampal c.  \\
154 & 6.56E-07 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
121 & 7.69E-06 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
\bottomrule
\end{tabular}
\end{table*}

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/group-slices}
    \caption{Mixed-effects group-level (N=14) GLM results. Significant clusters
        (Z>3.4, p<0.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
        head template (grey).
        Light grey: The audio-description's field-of-view
        (cf. \citep{hanke2014audiomovie}).
        Blue: the primary $t$-contrast for the audio-description comparing
        geometry-related nouns to non geometry-related nouns spoken by the
        audio-description's narrator (\texttt{geo, groom > all non-geo}).
        Red: the primary $t$-contrast for the movie comparing cuts to a new
        setting with cuts to a familiar perspective (\texttt{vse\_new >
        vpe\_old)}.
        Black: outline of overlapping individual PPA ROIs.
        \citep{sengupta2016extension}.}
    \label{fig:group-slices}
\end{figure*}

@@

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
    \caption{Fixed-effects individual-level GLM results (Z>3.4, p<0.05
        cluster-corrected). The brains of the 14 subjects are aligned via
        non-linear transformation to a study-specific T2* group template that is
    co-registered to the MNI152 template with an affine transformation (12
degrees of freedom) to facilitate comparisons across subjects.
        Light grey: The audio-description's field-of-view
        (cf. \citep{hanke2014audiomovie}).
        Blue: the primary $t$-contrast for the audio-description comparing
        geometry-related nouns to non geometry-related nouns spoken by the
        audio-description's narrator (\texttt{geo, groom > all non-geo}).
        Red: the primary $t$-contrast for the movie comparing cuts to a new
        setting with cuts to a familiar perspective (\texttt{vse\_new >
        vpe\_old)}.
        Black: outline of subject-specific PPA ROI.}

\label{fig:subs-thresh-ppa}
\end{figure*}

@@

\todo[inline]{I consider tables of significant clusters for every contrast as
overkill. One contrast, the ``primary contrast'', is appropriate.}

\subsection{stability contrasts}

% why we did different contrasts
We tested a variety of contrasts to ensure\dots ???

% results
The overlap of significant clusters of the 7 (well actually 8) contrast for the
audio-description, and 5 contrasts computed for the movie can be found in Figure
\ref{fig:stability-slices}.

% AO
\todo{alle noch einmal im einzelnen angucken; was ist mit COPE 8, der ist in der
Abb. nicht drin; zeigt (noch) einer keine sign. cluster?}
% PPA
Six of seven AO contrasts show significant bilateral clusters in anterior
regions of the group PPA overlap (which is temporal occipital fusiform gyrus
regarding to co-registered Harvard-Oxford Cortical Structural Atlas).
% Precuneus = retrosplenial cortex ?
Six of seven contrasts show significant clusters in the ventral precuneus /
retrosplenial cortex (RSC).

% AV
% PPA
All five AV contrasts yielded significant bilateral clusters in (temporal)
occipital, fusiform cortex showing congruency with the group overlap of
individual PPA ROIs.
% Lingual Gyrus
Homologous clusters of three contrasts extend further into lingual gyrus.
% RSC
Three contrasts show significant bilateral clusters in RSC.
% LOC
Four contrasts show significant bilateral clusters in lateral occipital cortex

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/stability-slices}
    \caption{Stability of contrasts. Overlap of significant clusters (Z>3.4;
        p<.05, cluster corrected) of contrasts created to isolate the PPA
        overlaid on the MNI152 T1-weighted head template (grey).
        Light grey: The audio-description's field-of-view
        (cf. \citep{hanke2014audiomovie}).
        Blue: contrasts 1-7 for the audio-description (see Table \ref{tab:ao-contrasts}.
        Red: contrasts 1-5 for the audio-visual movie (see Table \ref{tab:av-contrasts}.
        Black: outline of overlapping individual PPA ROIs
        \citep{sengupta2016extension}.}
    \label{fig:stability-slices}
\end{figure*}

@@

% Discussion explains how results fill gap identified in intro
% provides caveats to the interpretation
% describes how paper advances the field by providing new opportunities.

% typically done by recapitulating the results, discussing limitations,
% and then revealing how the central contribution may catalyze future progress.

% first discussion paragraph is special in that it generally summarizes the
% important findings from the results section -> give gist of results

% following paragraphs in the discussion section starts by describing an area of weakness or strength of the paper.
% It then evaluates the strength or weakness by linking it to the
% relevant literature.

% Discussion paragraphs often conclude by describing a clever, informal way of perceiving the contribution or by discussing future directions that can extend the contribution.

% For example, the first paragraph may summarize the results, focusing on their meaning.

% The second through fourth paragraphs may deal with potential weaknesses and with how the literature alleviates concerns or how future experiments can deal with these weaknesses.

% The fifth paragraph may then culminate in a description of how the paper moves
% the field forward.

%Step by step, the reader thus learns to put the paper’s conclusions into the right context.
